Limited evidence for widespread heterogeneity in psychology

### 2018-06-28 writing/appendixA-heterogeneity.rmd
Added rough .rmd drafts of appendices

---
title: "Figures"
author: "Anton Ohlsson Collentine"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.asp = 1.3)
```

```{r load packages, data and source helper functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(cowplot)){install.packages("cowplot")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #Plot data
library(cowplot) #Combine several plots into one

@@

source("helper_functions_tables_figures.r") #Load functions to prep data for figures
```

```{r transform_df}
#Transform effect sizes to raw correlations
#'transform_MA' is a sourced function
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe

```{r MA_df}
summarizer <- function(x){
  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1)) #estimates out
}
#Default method of metafor for calculating H2 is truncated at one. Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1). This method computes H2 as originally specified by Higgins & Thompson instead of using the more general method of metafor (see ?print.rma.uni).

#Higgins, J., & Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. Statistics in medicine, 21(11), 1539-1558.

res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(z = abs(z)) #Absolute values since we are interested in effect size rather than direction
```

```{r plot_res}

# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(I^2," index", sep = ""))) +
  scale_x_continuous(name = "Effect size (Fisher's z)")

# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(H^2," index", sep = ""))) +
  scale_x_continuous(name = "Effect size (Fisher's z)")

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
effect_het
# save_plot("../figures/effect-het.png", effect_het,
          # nrow = 2, base_aspect_ratio = 1.3, dpi = 600)

```{r robustness, results="hide"}
##Excluding anchoring effects
dropped_anchoring <- res2 %>%
  filter(!grepl("Anchoring", effect))

summary(lm(I2 ~ z, data = dropped_anchoring))
#b = 87.87, R2 = .51

```{r Plot_tau_against_I2, fig.asp = 0.618}
dat3 <- readRDS("../data/tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

#combined line plot gives good overview. Point version of the same is also interesting.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black"))

# ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)

@@

```{r Density_plot, fig.asp= 0.618}
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

@@

# ggsave("../figures/density-I2.png", dpi = 600, height =  4 , width = 6.47)
```

>>>>

---
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.asp = 0.618)
```

```{r load packages, data and source helper functions}
if(!require(readr)){install.packages("readr")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(purrr)){install.packages("purrr")}
if(!require(metafor)){install.packages("metafor")}

library(readr) #To load data
library(dplyr) #For data transformation
library(ggplot2) #Plot data
library(purrr) #For data iteration
library(metafor) #To run meta-analyses

@@

source("../code/helper_functions_tables_figures.r") #Load functions to prep data for figures
```

Appendix A - Sensitivity analysis of effect size for simulations

In our main results we simulated data to estimate type I error and power using an average effect size of zero. As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity. However, as a sensitivity analysis we in the Appendix analyze the same data, but generated with an average 'medium' effect size as defined by Cohen (1988).

Table A1.

_Type I error and power for data with an average 'medium' effect size_
```{r table_results}
dens <- readRDS("../data/power_simulation_results.RDS") #very large if saved as .csv
names(dens) <-  sort(unique(dat$effect))

#Summary of results. These are incorporated into the main table in the paper, see tables.rmd
I2_ci_lb <- dens %>% 
  bind_rows(.id = "effect") %>% 
  group_by(effect, tau_index) %>% 
  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
  ungroup() %>% 
  tidyr::spread(key = tau_index, value = power) %>% #prep for table
  rename(zero = '1', small = '2', medium = '3', large = '4')
```

```{r}
knitr::kable(I2_ci_lb, digits = 2)
```

Some comments on type I errors and power in Table A1.Subsequently comments on Figure A1.

```{r Plot_tau_against_I2, fig.asp = 0.618}
dat3 <- readRDS("../data/appendixA_tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black"))

@@

_Figure A1._

Here some comments on Figure A2.
```{r Density_plot, fig.asp= 0.618}
dens <- readRDS("../data/appendixA_power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

@@

_Figure A2._

Finally, conclusions from sensitivity analysis.
